Viscous Transport in Eroding Porous Media

### 2019-05-08 docs/transport/erosion_transport.tex
working on early sections

\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} \newcommand{\secref}[1]{\ref{#1}}
\newcommand{\Cdb}{\mbox{$\mathbb{C}$}}
\newcommand{\Rdb}{\mbox{$\mathbb{R}$}}

\newcommand{\D}{\mbox{${\mathcal D}$}}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\usepackage{float}
\input{preambles.tex}
\begin{document}

@@

% OTHER TITLE POSSIBILITIES
% Viscous Erosion in Porous Media (change 'in' to 'of'?)
% A fast and accurate method for viscous erosion of a 2D porous medium
% A boundary-integral method for viscous erosion of a porous medium
% A computational framework to simulate the viscous erosion of a porous medium

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing on our previous work~\cite{qua-moo2018}, we use a completed
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) ds_\yy,
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\eeta$ is an unknown
density function.  The double-layer potential itself can not represent
all solutions of the incompressible Stokes equations.  Therefore, we
complete the integral equation formulation following the work of Power
and Miranda~\cite{pow-mir1987}.  The completion depends on the
Stokeslets and rotlets
\begin{align}
  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \qquad
  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
\end{align}
where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
\|\rr\|$.  Then, the solution of the Stokes equation is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx),
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
    \NN_0(\eeta](\xx), \qquad \xx \in \bd\Omega, \\
  \lambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy) ds_\yy \qquad \ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp  \eeta(\yy) ds_\yy 
    \qquad \ell = 1,\ldots,M.
\end{align}

We will apply a quadrature rule that requires that the double-layer
potential representations of the velocity, shear stress, pressure, and
vorticity are written in terms of the Cauchy integral and its first two
derivatives
\begin{align}
  \label{eqn:Cauchy}
  v(x) &= \frac{1}{2\pi i} \int_\Gamma 
    \frac{\tau(y)}{x - y} dy, \\
  v'(x) &= -\frac{1}{2\pi i} \int_\Gamma 
    \frac{\tau(y)}{(x - y)^2} dy, \\
  v''(x) &= \frac{2}{2\pi i} \int_\Gamma 
    \frac{\tau(y)}{(x - y)^3} dy.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Velocity}
The Stokes double-layer potential can be written as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta)ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy,
\end{align}
and this formulation is convenient since each of the integrals can be
written as a Laplacian double-layer potential,
\begin{align}
  \DD[\tau](\xx) = -\frac{1}{2\pi} \int_{\Gamma} \pderiv{}{\nn_\yy}
    \log(\rho) \tau(\yy) ds_\yy.
\end{align}
Finally, by identifying $\RR^2$ with $\CC$, for purely real $\tau$, the
Laplacian double-layer potential can be written as the real part of a
Cauchy integral
\begin{align}
  \DD[\tau](x) = \Re (v(x)),
  \qquad \text{where} \qquad
  v(x) = \frac{1}{2\pi i} \int_\Gamma \frac{\tau(y)}{x - y} dy.
\end{align}
Therefore, the Stokes double-layer potential can be written as five
Cauchy integrals and their derivatives with the density functions $\yy
\cdot {\color{red}\eeta}$, $\eta_1$, and $\eta_2,$
{\color{red}
\begin{align}
 u_1(\xx)&= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
           -x_1\Re (v'[\eta_1](x)) -x_2\Re (v'[\eta_2](x)),\\
 u_2(\xx)&= \Re (v[\tau_2](x)) - \operatorname{Im} (v'[\yy\cdot\eeta](x)) 
       +x_1\operatorname{Im} (v'[\eta_1](x)) 
      +x_2\operatorname{Im} (v'[\eta_2](x)),
\end{align}
where
\begin{align*} 
\DD[\eeta](\xx)=(u_1(\xx),u_2(\xx)), \,\, 
\xx=(x_1,x_2), \,\,
\tau_1=(\eta_1+i\eta_2)\frac{\Re \, n}{n}, \text{ and }
\tau_2=(\eta_1+i\eta_2)\frac{\operatorname{Im} n}{n}.
\end{align*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
Since the rate of erosion is proportional to the shear stress, we also
require the gradient of the Stokes double-layer potential $\nabla
\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the gradient
of of the double-layer potential velocity is
{\color{red}
\begin{align}
 \nabla\D[\eeta] (\xx)=
\left[
\begin{matrix}
\displaystyle\frac{\partial u_1(\xx)}{\partial x_1} & 
\displaystyle\frac{\partial u_1(\xx)}{\partial x_2}\\ \\
\displaystyle\frac{\partial u_2(\xx)}{\partial x_1} & 
\displaystyle\frac{\partial u_2(\xx)}{\partial x_2}
\end{matrix}
\right],
\end{align}
where 
\begin{align}
\frac{\partial u_1(\xx)}{\partial x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 
           -\Re (v'[\eta_1](x)) -x_1\Re (v''[\eta_1](x))-x_2\Re (v''[\eta_2](x)),\\
\frac{\partial u_1(\xx)}{\partial x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 
      - \operatorname{Im} (v''[\yy\cdot\eeta](x)) 
       +x_1\operatorname{Im} (v''[\eta_1](x)) 
       -\Re (v'[\eta_2](x))
      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
\frac{\partial u_2(\xx)}{\partial x_1}&= \Re (v'[\tau_2](x)) 
      -\operatorname{Im} (v''[\yy\cdot\eeta](x)) 
       +\operatorname{Im} (v'[\eta_1](x))
       +x_1\operatorname{Im} (v''[\eta_1](x)) 
      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
\frac{\partial u_2(\xx)}{\partial x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
      -\Re (v''[\yy\cdot\eeta](x)) 
       +x_1\Re (v''[\eta_1](x)) 
      +\operatorname{Im} (v'[\eta_2](x)
      +x_2\Re (v''[\eta_2](x)).
\end{align}
%\begin{align}
%  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
%    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
%  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
%    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
%  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
%      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
%  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
%      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
Then, the deformation tensor can be written in terms of Cauchy integrals
\todo[inline]{For S-H to fill in}
\begin{align}
  \ssigma = \frac{1}{2} 
    \left(\nabla \DDD[\eeta] + \nabla^T \DDD[\eeta] \right) 
      \nn \cdot \ss = \ldots
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Vorticity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Pressure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A standard discretization of these equations approximates the
double-layer potential with the trapezoid rule.  This quadrature rule is
appropriate if the integrands are sufficiently smooth, where the
smoothness depends on the number of discretization points.  However,
given a fixed resolution, if the target point $\xx$ is too close to $\bd
\Omega$, the trapezoid rule becomes inaccurate and the overall method
becomes unstable.  There have been a variety of near-singular
integration schemes developed, and we extend a method first outlined by
Barnett et al.~\cite{bar-wu-vee2015} which we will call the {\em
Barycentric quadrature rule}.  Here, we briefly describe this quadrature
method, and then derive a necessary extension to simulate erosion.

Since we are able to write on all our quantities of interest in terms of
a Cauchy integral and its derivatives, we only require a near-singular
integration method for equation~\eqref{eqn:Cauchy}.  A quadrature scheme
for $v(x)$, for a target point $x$, is
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^N 
    w_j \frac{\tau(y_j)}{x - y_j},
\end{align}
where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
quadrature nodes.  If the trapezoid rule is used, the quadrature rule
has spectral accuracy.  However, for a fixed resolution $N$, the error
grows without bound as $x$ approaches $\Gamma$.  As outline by Barnett
et al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
Barycentric quadrature rule
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
  v'(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
\end{align}
is used, where $x$ is a target point that is interior to $\Gamma$,
and $v_j^-$ is the value of $v(y_j)$.  Modifications of this formula
exist if $x$ is exterior to $\Gamma$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
In order to simulate erosion, we require the deformation gradient which
means that a quadrature rule for $v''(x)$ is required.  Using the same
techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
quadrature rule for the second derivative can be constructed using the
identities
{\color{red}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.

>>>>

\input{preambles.tex}
\begin{document}

@@

% OTHER TITLE POSSIBILITIES
% ???

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing on our previous work~\cite{qua-moo2018}, we use a completed
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
double-layer potential can be as the sum of the Laplace double-layer
potential and its gradient.  By identifying $\xx,\yy \in \RR^2$ with the
points $x,y \in \CC$, the Laplace double-layer potential for a
real-valued density function $\eta$ can also be written as the real part
of the Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy = 
  \Re \left( \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy \right).
\end{align}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and its first derivative.  In addition, we also require
expressions for the derivative of the velocity field which can be
written in terms of a Cauchy integral and its first two derivatives.
Therefore, we introduce the notation
\begin{align}
  \label{eqn:cauchy}
  v[\eta](x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,  \quad
  v'[\eta](x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^2} \, dy, \quad
  v''[\eta](x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^3} \, dy.
\end{align}
To simplify notation, whenever it will not cause confusion, we exclude
$\tau$ and instead write $v(x)$, $v'(x)$, and $v''(x)$.

The Stokes double-layer potential itself can not represent all solutions
of the incompressible Stokes equations.  Therefore, we complete the
integral equation formulation following the work of Power and
Miranda~\cite{pow-mir1987}.  The completion depends on the Stokeslets
and rotlets
\begin{align}
  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2} \right), \quad
  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
\end{align}
where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
\|\rr\|$.  Then, the solution of the Stokes equation is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx),
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
    \NN_0(\eeta](\xx), \quad \xx \in \bd\Omega, \\
  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy) ds_\yy \quad \ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy) ds_\yy 
    \quad \ell = 1,\ldots,M,
\end{align}
where $\ff$ is the prescribed Dirichlet boundary condition of the
velocity on the outer wall and eroding bodies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
\end{align}
All these integrals but the first are a gradient of a Laplace layer
potential with the density functions $\eta_1$, $\eta_2$, and $\yy \cdot
\eeta$.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued
densities~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)),\\
  u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of $\nn \in \RR^2$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
To compute the rate of erosion, we must compute the shear stress of the
double-layer potential
\begin{align}
  \tau(\xx) = \left(\nabla \DDD[\eeta](\xx) + 
    \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
\end{align}
where $\nn$ and $\ss$ are the unit normal and tangent vectors at $\xx$,
respectively.  Each term of the gradient of the velocity field can be
written in terms of Cauchy integrals as
\todo[inline]{not clear enough how we got these equations.  Need to show
how we do one of them and say the rest are calculated similarly.}
\begin{align}
  \pderiv{u_1}{x_1}(\xx) &= \Re (v'[\tau_1](x)) + 
    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
  \pderiv{u_1}{x_2}(\xx) &= - \Im (v'[\tau_1](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v''[\eta_1](x)) - 
    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_1}(\xx) &= \Re (v'[\tau_2](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
    x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_2}(\xx) &= -\Im (v'[\tau_2](x)) - 
    \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
    \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
\end{align}
\todo[inline]{S-H: last term seems to be missing an $x_1$.  Some of the
other terms seem to be a bit off.  It might be partially my fault from
when I updated some of the tex.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Vorticity}
Having calculated all derivatives of the double-layer potential, the
vorticity can written in terms of Cauchy integrals.  In particular
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\end{align}
\todo[inline]{For S-H to fill in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Pressure}
The pressure of the double-layer potential is
\begin{align}
  p(\xx) = -\frac{1}{\pi} \int_{\bd\Omega} \frac{1}{\rho^2}
    \left(1 - 2 \frac{\rr \otimes \rr}{\rho^2} \right) \nn
    \cdot \eeta(\yy) \, ds_\yy.
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We are interested in computing the velocity, shear stress, vorticity,
and pressure of the Stokes double-layer potential.  We have shown that
all these quantities can be written in terms of Cauchy integrals and its
first two derivatives.  Therefore, we require quadrature methods to
evaluate the expressions in equation~\eqref{eqn:cauchy}.  The trapezoid
rule is appropriate if the integrands are sufficiently smooth, where the
smoothness depends on the number of discretization points.  However,
given a fixed resolution, if the target point $\xx$ is too close to $\bd
\Omega$, the trapezoid rule becomes inaccurate and the overall method is
unstable.  There have been a variety of near-singular integration
schemes developed, and we extend a method first outlined by Barnett et
al.~\cite{bar-wu-vee2015} which we will call the {\em Barycentric
quadrature rule}.  Here, we briefly describe this quadrature method, and
then derive a necessary extension to simulate erosion.

The Barycentric quadrature rule starts with a general quadrature rule
for $v(x)$
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^N 
    w_j \frac{\tau(y_j)}{x - y_j},
\end{align}
where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
quadrature nodes.  We will use the trapezoid rule because of its
superior accuracy when $x$ is sufficiently far from $\Gamma$.  However,
for a fixed resolution $N$, the error grows without bound as $x$
approaches $\Gamma$.  As outline by Barnett et
al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
Barycentric quadrature rule
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}
  \quad \text{and} \quad
  v'(x) \approx \frac{\sum\limits_{j=1}^N 
    \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
\end{align}
is used, where $x$ is a target point that is interior to $\Gamma$,
and $v_j^-$ is the value of $v(y_j)$.  Modifications of this formula
exist if $x$ is exterior to $\Gamma$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
developed~\cite{bar-wu-vee2015}, this work requires a similar quadrature
rule for $v''(x)$.  We mimic the approach developed
in~\cite{bar-wu-vee2015} by starting with the identities
\todo[inline]{S-H: How do we get these identities?}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
{\color{red}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.
